### 2017-04-05 paper/evaluation.tex
added missing values from fig 10

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.
From the \numMedLong{} projects, we identified \numProjectsPar{}
projects with the parallel execution modes \ForkSeq{} and
\ParClassParMeth{} enabled by default.
Figure~\ref{tab:freqmodes-dynamic} summarizes our findings. The column
``Group'' indicates the test cost group (see
Figure~\ref{fig:rq1-barplot}), the column ``Subject'' indicates the
name of the project, the column ``\# of modules'' indicates the number
of modules with tests in the default execution, and the column
``Mode'' indicates the corresponding parallelization mode.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        Medium & Apache Flink & - & - \\%
        Medium & BounceStorage Chaos HTTP Proxy & - & -\\%
        Medium & Hazelcast Jet & - & -\\%
        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        Medium & Javaslang & - & \ParClassParMeth{}\\%
        Medium & Jcabi Github & - & \ParClassParMeth{}\\%
        Medium & Spotify Helios & - & - \\%
        \bottomrule%
    \end{tabular}}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{figure}

>>>>

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.
From the \numMedLong{} projects, we identified \numProjectsPar{}
projects with the parallel execution modes \ForkSeq{} and
\ParClassParMeth{} enabled by default.
Figure~\ref{tab:freqmodes-dynamic} summarizes our findings. The column
``Group'' indicates the test cost group (see
Figure~\ref{fig:rq1-barplot}), the column ``Subject'' indicates the
name of the project, the column ``\# of modules'' indicates the number
of modules with tests in the default execution, and the column
``Mode'' indicates the corresponding parallelization mode.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        Medium & Apache Flink & 74 & \ForkSeq{} \\%
        Medium & BounceStorage Chaos HTTP Proxy & 1 & \ParClassSeqMeth{}\\%
        Medium & Hazelcast Jet & 7 & \ForkSeq{}\\%
        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        Medium & Spotify Helios & 8 & \ForkSeq{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{figure}
